\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{enumitem}


% Inputting Python code
\usepackage[dvipsnames]{xcolor}
\definecolor{textblue}{rgb}{.2,.2,.7}
\definecolor{textred}{rgb}{0.54,0,0}
\definecolor{textgreen}{rgb}{0,0.43,0}
\usepackage{upquote}
\usepackage{listings}
\lstset{
    language=Python, 
    tabsize=4,
    basicstyle={\ttfamily},
    keywordstyle=\color{textblue},
    commentstyle=\color{textgreen},
    stringstyle=\color{textred},
    frame=none,
    columns=fullflexible,
    keepspaces=true,
    showstringspaces=false,
    xleftmargin=-15mm, % manual adjustment, figure out permanent solution
}


\definecolor{royalblue}{RGB}{65,105,225} % Defining royal blue
% colored links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=royalblue,
    }


% Drawing figures
\usepackage{tikz}
\usetikzlibrary{calc, shapes.symbols}

% Colored Boxes
\usepackage{tcolorbox}
\tcbuselibrary{skins,hooks}
\usetikzlibrary{shadows}
\usepackage{lipsum}

% Quotes
\usepackage{epigraph}

%Images
\usepackage{graphicx}
    \usepackage{subcaption}
    \usepackage{float}

%Formatting and Spacing
\setitemize[1]{noitemsep, parsep = 5pt, topsep = 5pt}
\setenumerate[1]{label = (\alph*), parsep = 1pt, topsep = 5pt}
\setlength\parindent{0pt}
\linespread{1.1}

\usepackage{bm}

% title
\title{\vspace{-1cm}CS 4540: Advanced Algorithms \\ Spring 2024}
\author{Sarthak Mohanty}
\date{}


\begin{document}

\maketitle

\vspace{-1cm}
\section*{Overview}

\section*{Problem 1}
    In this problem, we will cover a state-of-the-art wave simulation for real-time rendering. I can't understate the importance of this: this was a seminal paper that generated literally a multimillion dollar application of fft.
    \begin{itemize}
        \item \href{https://www.youtube.com/watch?v=kGEqaX4Y4bQ}{FFT Ocean Waves in Unity} based on \href{https://people.computing.clemson.edu/~jtessen/reports/papers_files/coursenotes2004.pdf}{Original FFT Ocean Waves Paper} This is literally state of the art in real-time wave simulation, even used in Sea of Thieves, see \href{https://dl.acm.org/doi/pdf/10.1145/3214745.3214820}{this talk}
        \item Most realistic implementation currently is by Fluid Flow 2, developed for Unreal Engine 5 and based on the \href{https://matthias-research.github.io/pages/publications/hfFluid.pdf}{this} 2010 paper.
        \item these approaches are all primarily mesh-based. There are rumors that Rockstar games has developed a node-based system in real-time for their upcoming GTA6, but these are just rumors and RAGE (their game engine) is closed-source anyway, so we may never know if this is the case.
    \end{itemize}

    The problem is as follows: 

    \begin{enumerate}
        \item \textbf{Gerstner waves} are the first model that can somewhat approximate the surface waves dynamics. Suppose we have a point on the wave's surface $\bm{x}$. Then the effect of a \textit{single} wave with amplitude $A$ displaces the point at time $t$ as follows\footnote{A subtle but important observation is that these calculations can be parallized.}:

        \begin{align*}
            \bm{x} &= \bm{x}_{0} - (\bm{k} / k)A\sin(\bm{k} \cdot \bm{x}_{0} - \omega t) \\
            y &= A\cos(\bm{k} \cdot \bm{x}_{0} - \omega t).
        \end{align*}
        Here the \textbf{wavevector} $\bm{k}$ is a horizontal vector that points in the direction of travel of the wave, and has magnitude $k$ related to the length of the wave $\lambda$ by $$k = 2\pi / \lambda.$$

        An image of a Gerstner wave is shown below in Figure 1.

        Of course, a single wave does us little good. Realistically, there will be multiple waves affecting a particle. We can model this as well: 

        \begin{align*}
            \bm{x} &= \bm{x}_{0} - \sum_{i = 1}^{N} (\bm{k}_{i} / k_{i})A_{i}\sin(\bm{k}_{i} \cdot \bm{x}_{0} - \omega_{i} t + \phi_{i}) \\
            y &= \sum_{i = 1}^{N} A_{i}\cos(\bm{k}_{i} \cdot \bm{x}_{0} - \omega_{i} t + \phi_{i}).
        \end{align*}

        Your task is to model this wave for times $t = [0, 1]$ using the waves given below. 
        \item While Gerstner waves alone can achieve great results, the leading simulators instead choose to represent the wave height motion as a sum of sinusoidal functions. This representation also us to calculate the displacements using ffts, which allow for computational efficiency.

        We begin with Euler's formula, which allows us to encapuslate the information from 

        Your task is to express the above expression as a DFT.

        \item Now that we have expressed the above expression, you can apply the fft algorithm.

        \item The waves produced by the fft methods so far have rounded peaks and troughs. However, we know from experience that waves are sharply peaked at their tops, and flattened at the bottoms.

        \item There is an issue. Right now we are generating a great wave simulation, but only over a small set of points. How do we do this for an entire ocean? It is unfeasible to do this calculation over say a grid that is $2048 \times 2048$, so we must come up with a different solution.

        \begin{itemize}
            \item Option 1: while the original tessendorf paper did address this issue, they did not meniton how to fix it.  do some research: figure out how this issue is circumvented or solved in real life. desribe and implement this solution
            \item Option 2: The solution is to cascade different fourier transforms with different patch lengths. Implement this solution. 
        \end{itemize}


        % for 2d

        % https://dododas.github.io/posts/2021/2021-01-17-matplotlib-waves/

        % for 3d

        % https://matplotlib.org/stable/gallery/animation/random_walk.html
        
    \end{enumerate}

    

\begin{tcolorbox}[enhanced,interior style={top color=Dandelion!20,bottom color=Dandelion!30}]
    Test
\end{tcolorbox}

\section*{Problem 2}
    Delauney Triangulation for mesh refinement.

\begin{tcolorbox}[enhanced,interior style={top color=Dandelion!20,bottom color=Dandelion!30}]
    Test
\end{tcolorbox}

\end{document}

# personal live demo

https://medium.com/@joshmarinacci/low-poly-style-terrain-generation-8a017ab02e7b